### 2023-11-19 sections/2-methods.tex
cite simev

We expect CAKES to perform well as the cardinality of datasets increases, and to explore this scaling behavior, we augmented datasets in the ANN-benchmarks suite by adding random points within a 
small noise threshold of existing points. This allowed us to isolate the effect of \emph{cardinality} on the performance of CAKES 
from that of other factors such as dimensionality, metric, or topological structure of the dataset.

>>>>

We expect CAKES to perform well as the cardinality of datasets increases, and to explore this scaling behavior, we augmented datasets in the ANN-benchmarks suite by adding random points within a 
small noise threshold of existing points; this technique has been used in a number of bioinformatics contexts~\cite{kumar2009augmented, kumar2010recognition, daniels2012smurflite, velasco2018combining, lu2020evolution}. This allowed us to isolate the effect of \emph{cardinality} on the performance of CAKES 
from that of other factors such as dimensionality, metric, or topological structure of the dataset.
